The \kplr\ Catalog: Systematic probabilistic parameter estimation for every \kepler\ planet candidate

### 2013-12-28 document/ms.tex

The basic idea is that we have some function $f(t)$ that returns the
instantaneous flux of the system at time $t$ but we would like to compute the
integrated flux over an exposure time \texp
\begin{eqnarray}
f_\mathrm{int}(t_0) &=& \int_{t_0-\texp/2}^{t_0+\texp/2} f(t) \dd t
\end{eqnarray}

>>>>

The basic idea is that we have some function $f(t)$ that returns the
instantaneous flux of the system at time $t$ but we would like to compute the
integrated flux over an exposure time \texp
\begin{eqnarray}
f_\mathrm{int}(t_0;\texp) &=& \int_{t_0-\texp/2}^{t_0+\texp/2} f(t) \dd t
    \quad.
\end{eqnarray}
Following Kipping, this can be approximated as
\begin{eqnarray}
f_\mathrm{int}(t_0;\texp) &\approx&
    \frac{f(t_0-\texp/3)+f(t_0)+f(t_0+\texp/3)}{3} \quad.
\end{eqnarray}
We extend this by recursively defining this approximation as
\begin{eqnarray}
f_\mathrm{int}(t_0;\texp) &\approx&
    \frac{f_\mathrm{int}(t_0-\texp/3;\texp/3)+f_\mathrm{int}(t_0;\texp/3)
          +f_\mathrm{int}(t_0+\texp/3;\texp/3)}{3}
\end{eqnarray}
where the recursive depth is set by a tolerance on
\begin{eqnarray}
\left | f(t_0-\texp/3)-2\,f(t_0)+f(t_0+\texp/3) \right | &\le& \epsilon
\end{eqnarray}
where $\epsilon$ is a free parameter quantifying the required accuracy of the
method.
